\subsection{Operation Model for oeCloseCrisis}

\label{OM-oeCloseCrisis}


The \msrcode{oeCloseCrisis} operation has the following properties:

	\begin{operationmodel}
	\addheading{Operation}
	\adddoublerow{oeCloseCrisis}{sent to indicate that a crisis should be considered as closed.}

	\addrowheading{Parameters}
	\addnumbereddoublerow{}{AdtCrisisID: dtCrisisID}{the identification information used to determine the crisis to close} 
	\addnumbereddoublerow{}{AdtCrisisID: dtCrisisID}{ } 

	\addrowheading{Return type}
	\addsinglerow{ptBoolean}

	\addrowheading{Pre-Condition (protocol)}
	\addnumberedsinglerow{PreP}{the system is started}
	\addnumberedsinglerow{PreP}{the actor logged previously and did not log out ! (i.e. the associated ctCoordinator instance is considered logged)}
		
	\addrowheading{Pre-Condition (functional)}
	\addnumberedsinglerow{PreF}{it is supposed that there exist one ctCrisis instance with the same \msrcode{id} attribute value as the one provided by the coordinator actor who wants to close.}

	\addrowheading{Post-Condition (functional)}
	\addnumberedsinglerow{PostF}{the ctCrisis class instance having the provided id is considered closed in the post state.}
	\addnumberedsinglerow{PostF}{There is no handler declared in the system as associated to the crisis.}
	\addnumberedsinglerow{PostF}{all the alert instances associated to this crisis do not belong any more to the system's post state.}
	\addnumberedsinglerow{PostF}{the coordinator actor is informed about the satisfaction of its request.}
	\addnumberedsinglerow{PostF}{an update of coordinator status and coordinator timing statistic for all administrators}

	\addrowheading{Post-Condition (protocol)}
	\addnumberedsinglerow{PostP}{none}
	\end{operationmodel}



	% ------------------------------------------
	% MCL Listing
	% ------------------------------------------
	\vspace{1cm}
	The listing~\ref{OM-actCoordinator-oeCloseCrisis-MCL-LST} provides the \msrmessir (MCL-oriented) specification of the operation.
	
	\scriptsize
	\vspace{0.5cm}
	\begin{lstlisting}[style=MessirStyle,firstnumber=auto,captionpos=b,caption={\msrmessir (MCL-oriented) specification of the operation \emph{oeCloseCrisis}.},label=OM-actCoordinator-oeCloseCrisis-MCL-LST]

	
	
	/* Post Functional:*/ 
	postF{let TheSystem:ctState in
	let AcoordStatisticUpdate: dtCoordStatistic in
	TheSystem.rnactAdministrator.rnInterfaceIN ^ieTimeStatisticUpdated(AcoordStatisticUpdate)}
	
	
	\end{lstlisting}
	\normalsize 
	
	
	
	
	% ------------------------------------------
	% PROLOG Listing
	% ------------------------------------------
	
	\vspace{1cm}
	The listing~\ref{OM-actCoordinator-oeCloseCrisis-PROLOG-LST} provides the \msrmessir (Prolog-oriented) implementation of the operation.
	
	\scriptsize
	\vspace{0.5cm}
	
	\lstinputlisting[style=MessirPrologStyle,firstnumber=auto,captionpos=b,caption={\msrmessir (Prolog-oriented) implementation of the operation \emph{oeCloseCrisis}.},label=OM-actCoordinator-oeCloseCrisis-PROLOG-LST]{../lu.uni.lassy.excalibur.examples.icrash.simulation/src/Operations/Environment/OUT/outactCoordinator-oeCloseCrisis.pl}
	\normalsize





